|

### 2019-09-06 inst/manuscript/candidaev_figures.Rmd
Switch CairoPDF back to grDevices pdf

```{r figure1, fig.width=7.1, fig.height=4, fig.path='figures/', dev=c('CairoPDF', 'CairoPS', 'tiff'), dev.args=f1_args, dpi=600}
# draw figure 1
ggarrange(f1a, 
          ggarrange(f1b, f1c, 
                    labels = c("B", "C"), 
                    ncol = 2,
                    nrow = 1, 
                    widths = c(1.8,1)), 
          labels = c("A", ""), 
          nrow = 2, 
          ncol = 1, 
          heights = c(1,1))
```

@@

```{r figure2, fig.width=7.1, fig.height=6, fig.path='figures/', dev=c('CairoPDF', 'CairoPS', 'tiff'),  dev.args=f2_args, dpi=600}
# draw figure 2
ggarrange(ggarrange(f2a1, f2a2, f2a3, f2a4, 
                    labels = c("A", "", "", ""), 
                    ncol = 4, 
                    nrow = 1, 
                    align = "v"), 
          ggarrange(f2b1, f2b2,
                    f2b3, f2b4, 
                    labels = c("B", rep("", 3)), 
                    ncol = 2, 
                    nrow = 2, 
                    align = "hv", 
                    common.legend = TRUE, 
                    legend = "right", 
                    widths = c(1,1), 
                    vjust = 1), 
          ncol = 1,
          nrow = 2, 
          heights = c(1,2))
```

@@

```{r figure3, fig.width=7.2, fig.height=6, fig.path='figures/', dev=c('CairoPDF', 'CairoPS', 'tiff'),  dev.args=f3_args, dpi=600}
# draw figure 3
ggarrange(f3_y, f3_a9, 
          f3_a1, f3_b, 
          labels = NULL, 
          ncol = 2, 
          nrow = 2, 
          common.legend = TRUE, 
          legend = "bottom", 
          align = "hv")
```

@@

```{r figure4, fig.width=7.1, fig.height=5, fig.path='figures/', dev=c('CairoPDF', 'CairoPS', 'tiff'),  dev.args=f4_args, dpi=600}
ggarrange(ggarrange(f4a, f4b,
                    labels = c("A", "B"),
                    ncol = 2,
                    nrow = 1),
          ggarrange(f4c, f4d,
                    labels = c("C", "D"),
                    ncol = 2,
                    nrow = 1, 
                    common.legend = TRUE,
                    legend = "right", 
                    align = "hv"),
          labels = NULL,
          ncol = 1,
          nrow = 2,
          heights = c(2, 3))
```

@@

```{r figure5, fig.height=6, fig.path='figures/', dev=c('CairoPDF', 'tiff'), dev.args=f5_args, dpi=600}
f5 <- png::readPNG("figures/figure5.png")

@@

```{r figure6, fig.width=2.5, fig.height=4, fig.path='figures/', dev=c('CairoPDF', 'CairoPS', 'tiff'), dev.args=f6_args, dpi=600}
ggarrange(f6a, f6b, 
          labels = c("A", "B"), 
          ncol = 1,
          nrow = 2)

@@

```{r figure7, fig.width=4, fig.height=3.6, fig.path='figures/', dev=c('CairoPDF', 'tiff'), dev.args=f7_args, dpi=600}
f7 <- png::readPNG("figures/figure7.png")

@@

```{r figure8, fig.width=7.2, fig.height=6, fig.path='figures/', dev=c('CairoPDF', 'tiff'), dev.args=f8_args, dpi=600}
f8 <- png::readPNG("figures/figure8.png")

>>>>

```{r figure1, fig.width=7.1, fig.height=4, fig.path='figures/', dev=c('pdf', 'CairoPS', 'tiff'), dev.args=f1_args, dpi=600}
# draw figure 1
ggarrange(f1a, 
          ggarrange(f1b, f1c, 
                    labels = c("B", "C"), 
                    ncol = 2,
                    nrow = 1, 
                    widths = c(1.8,1)), 
          labels = c("A", ""), 
          nrow = 2, 
          ncol = 1, 
          heights = c(1,1))
```

@@

```{r figure2, fig.width=7.1, fig.height=6, fig.path='figures/', dev=c('pdf', 'CairoPS', 'tiff'),  dev.args=f2_args, dpi=600}
# draw figure 2
ggarrange(ggarrange(f2a1, f2a2, f2a3, f2a4, 
                    labels = c("A", "", "", ""), 
                    ncol = 4, 
                    nrow = 1, 
                    align = "v"), 
          ggarrange(f2b1, f2b2,
                    f2b3, f2b4, 
                    labels = c("B", rep("", 3)), 
                    ncol = 2, 
                    nrow = 2, 
                    align = "hv", 
                    common.legend = TRUE, 
                    legend = "right", 
                    widths = c(1,1), 
                    vjust = 1), 
          ncol = 1,
          nrow = 2, 
          heights = c(1,2))
```

@@

```{r figure3, fig.width=7.2, fig.height=6, fig.path='figures/', dev=c('pdf', 'CairoPS', 'tiff'),  dev.args=f3_args, dpi=600}
# draw figure 3
ggarrange(f3_y, f3_a9, 
          f3_a1, f3_b, 
          labels = NULL, 
          ncol = 2, 
          nrow = 2, 
          common.legend = TRUE, 
          legend = "bottom", 
          align = "hv")
```

@@

```{r figure4, fig.width=7.1, fig.height=5, fig.path='figures/', dev=c('pdf', 'CairoPS', 'tiff'),  dev.args=f4_args, dpi=600}
ggarrange(ggarrange(f4a, f4b,
                    labels = c("A", "B"),
                    ncol = 2,
                    nrow = 1),
          ggarrange(f4c, f4d,
                    labels = c("C", "D"),
                    ncol = 2,
                    nrow = 1, 
                    common.legend = TRUE,
                    legend = "right", 
                    align = "hv"),
          labels = NULL,
          ncol = 1,
          nrow = 2,
          heights = c(2, 3))
```

@@

```{r figure5, fig.height=6, fig.path='figures/', dev=c('pdf', 'tiff'), dev.args=f5_args, dpi=600}
f5 <- png::readPNG("figures/figure5.png")

@@

```{r figure6, fig.width=2.5, fig.height=4, fig.path='figures/', dev=c('pdf', 'CairoPS', 'tiff'), dev.args=f6_args, dpi=600}
ggarrange(f6a, f6b, 
          labels = c("A", "B"), 
          ncol = 1,
          nrow = 2)

@@

```{r figure7, fig.width=4, fig.height=3.6, fig.path='figures/', dev=c('pdf', 'tiff'), dev.args=f7_args, dpi=600}
f7 <- png::readPNG("figures/figure7.png")

@@

```{r figure8, fig.width=7.2, fig.height=6, fig.path='figures/', dev=c('pdf', 'tiff'), dev.args=f8_args, dpi=600}
f8 <- png::readPNG("figures/figure8.png")

### 2019-09-06 inst/manuscript/candidaev_supplement.Rmd
Switch CairoPDF back to grDevices pdf

```{r figureS1, fig.cap=fS1_cap, fig.width=5.45, fig.height=6, fig.path='figures/', dev=c('CairoPDF', 'tiff'), dev.args=fS1_args, dpi=600}
# construct figure 1
fS1_cap <- "\\textbf{Schematic of the workflow used for the isolation and 
           proteomic analysis of \\textit{C. albicans} EVs and the selection 
           of EV protein markers.} Steps 1 to 6 were performed for each of the 
           four strains examined in this study: DAY286 yeast, ATCC90028 yeast, 
           ATCC10231 yeast, and DAY286 biofilm. The results from the four 
           seperate analyses were combined (step 7) to identify proteins which 
           commonly appeared as EV marker candidates. The MISEV2018 criteria 
           for protein content-based EV characterisation and other 
           considerations were used to select the best \\textit{C. albicans} 
           EV marker proteins."

@@

```{r figureS2, fig.cap=fS2_cap, fig.height=5, fig.width=5, fig.path='figures/', dev=c('CairoPDF', 'CairoPS', 'tiff'), dev.args=fS2_args, dpi=600}
fS2_cap <- c("\\textbf{Size distribution of \\textit{C. albicans} EVs as 
              determined by nanoparticle tracking analysis (NTA).} A line plot 
              for each EV biological replicate from each strain is shown. Each 
              line plots represents the average of three technical replicates 
              and the dashed grey lines indicate 100 nm.")

>>>>

```{r figureS1, fig.cap=fS1_cap, fig.width=5.45, fig.height=6, fig.path='figures/', dev=c('pdf', 'tiff'), dev.args=fS1_args, dpi=600}
# construct figure 1
fS1_cap <- "\\textbf{Schematic of the workflow used for the isolation and 
           proteomic analysis of \\textit{C. albicans} EVs and the selection 
           of EV protein markers.} Steps 1 to 6 were performed for each of the 
           four strains examined in this study: DAY286 yeast, ATCC90028 yeast, 
           ATCC10231 yeast, and DAY286 biofilm. The results from the four 
           seperate analyses were combined (step 7) to identify proteins which 
           commonly appeared as EV marker candidates. The MISEV2018 criteria 
           for protein content-based EV characterisation and other 
           considerations were used to select the best \\textit{C. albicans} 
           EV marker proteins."

@@

```{r figureS2, fig.cap=fS2_cap, fig.height=5, fig.width=5, fig.path='figures/', dev=c('pdf', 'CairoPS', 'tiff'), dev.args=fS2_args, dpi=600}
fS2_cap <- c("\\textbf{Size distribution of \\textit{C. albicans} EVs as 
              determined by nanoparticle tracking analysis (NTA).} A line plot 
              for each EV biological replicate from each strain is shown. Each 
              line plots represents the average of three technical replicates 
              and the dashed grey lines indicate 100 nm.")
